Modeling memory and taxis to analyze migrations

### 2021-01-06 code/StrategicVsTactical_PartI_v2.Rmd
First commit - of the project to date

```{r}
source("functions.R")
```

@@

```{r setupEnvironment}

getSinePop <- function(Time, X, X.max, peak.max, peak.min, sd){
  pop <- outer(Time, X,
                     function(t,x) 
                       dnorm(x, mean = X.max/2 + (peak.max-peak.min) / 2 * sin( 2*(t * pi)/max(Time)),sd = sd))
  pop <- apply(pop, 1, function(x) x/sum(x)) %>% t
  pop / mean(diff(X))
}

@@

```{r memoryOnly, fig.height = 5, fig.width = 10}
dx <- .5
parameters <- c(epsilon = 5, alpha = 0, beta = 5e2, lambda = 0, dx = dx)
eval <- FALSE
if(eval){
  MemSim <- runManyYears(pop.Year1, Time, Resource = fixed.Resource, Parameters = parameters, n.years = 3)
  save(MemSim, file = "../results/MemSim.rda")
} else load("../results/MemSim.rda")

>>>>

```{r}
source("functions2.R")
```

@@

```{r setupEnvironment}
getSinePop <- function(Time, X, X.max, peak.max, peak.min, sd){
  pop <- outer(Time, X,
                     function(t,x) 
                       dnorm(x, mean = X.max/2 + (peak.max-peak.min) / 2 * sin( 2*(t * pi)/max(Time)),sd = sd))
  pop <- apply(pop, 1, function(x) x/sum(x)) %>% t
  pop / mean(diff(X))
}

@@

```{r}
ForagingMemoryModel <- function(t, y, parms, resource, pop_lag){
  tran.1D(C = y, D = parms["epsilon"], 
          flux.up = 0, flux.down = 0, 
          v = parms["alpha"] * diff(resource)/parms["dx"] +  
            parms["gamma"] * diff(y)/parms["dx"] +
            parms["beta"] * diff(pop_lag)/parms["dx"], 
          dx = parms["dx"])
}

ForagingMemoryModel <- function(t, y, parms, resource, pop_lag){
  tran.1D(C = y, D = parms["epsilon"], 
          flux.up = 0, flux.down = 0, 
          v = parms["alpha"] * diff(resource)/parms["dx"] +  
            parms["gamma"] * diff(y)/parms["dx"] +
            parms["beta"] * diff(pop_lag)/parms["dx"], 
          dx = parms["dx"])
}

```{r memoryOnly, fig.height = 5, fig.width = 10}
dx <- .5
parameters <- c(epsilon = 5, alpha = 0, beta = 5e2, gamma = 20, lambda = 0, dx = dx)

eval <- FALSE
if(eval){
  MemSim <- runManyYears(pop.Year1, Time, Resource = fixed.Resource, Parameters = parameters, n.years = 3)
  save(MemSim, file = "../results/MemSim.rda")
} else load("../results/MemSim.rda")
